### 2025-01-28 paper/icml25/first/sects/background.tex
clarify some notion on 2.2

\subsection{Neural Networks}
A neural network is a function $f_{\theta}:\mathbb{R}^n\rightarrow\mathbb{R}^m$ parameterized by $\theta$ that maps an input vector $x\in\mathbb{R}^n$ to an output vector $y\in\mathbb{R}^m$. The parameters $\theta$ of the network are learned by minimizing a loss function $\mathcal{L}_\theta$ with respect to the training data.

>>>>

\subsection{Neural Networks}
A neural network is a function $f_{\theta}:\mathbb{R}^n\rightarrow\mathbb{R}^m$ parameterized by its weights $\theta$, which maps an input vector $x\in\mathbb{R}^n$ to an output vector $y\in\mathbb{R}^m$. 
The network parameters $\theta$ are optimized by minimizing the loss function $\mathcal{L}_\theta$, which quantifies the discrepancy between the network's predictions and the target outputs based on the training data.
